\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction}
\markboth{General Introduction}{}

The world of telecommunications forms the invisible backbone that connects billions of people across the globe, enabling communication, commerce, and social interaction that define modern society. Behind every phone call, text message, or internet connection lies a complex infrastructure of mobile network sites, base stations, and sophisticated equipment that must operate seamlessly 24 hours a day.

For telecommunications operators, managing this critical infrastructure presents significant challenges. Network sites scattered across vast geographical areas require constant monitoring, preventive maintenance, and rapid response to failures that could disrupt essential services for entire communities. Traditional management approaches often rely on manual processes and disconnected systems, leading to delayed fault detection, inefficient resource allocation, and ultimately, service interruptions that impact people's daily lives.

In an era where reliable communication has become a fundamental human need, particularly highlighted during recent global events, the importance of robust network infrastructure management cannot be overstated. Citizens depend on mobile networks for emergency services, remote work, education, and maintaining social connections with loved ones.

This final year project addresses these challenges by developing TelecomOps, a comprehensive web-based application designed for the management, operation, maintenance, and auditing of mobile network sites. Using modern technologies including Next.js, TypeScript, and Supabase, the solution provides telecommunications operators with the tools necessary to ensure reliable service delivery to their communities.

The project employs Scrum methodology across six development sprints, covering site management, equipment monitoring, fault detection, alerting systems, reporting capabilities, and deployment practices. Through this systematic approach, TelecomOps aims to transform how telecommunications infrastructure is managed, ultimately improving service reliability for the millions of users who depend on these networks daily.

This dissertation presents the complete development journey, from initial problem analysis through final deployment, demonstrating how modern software engineering practices can address real-world challenges that directly impact society.